Democracy, Public Support, and Measurement Uncertainty

### 2021-07-26 paper/dcpo_demsupport.Rmd
new output code revised

#load(here("data", "pure_cls_ajps.rda")) 
#load(here("data", "pure_cls_apsr.rda")) 
load(here("data", "correct_cls_ajps.rda"))
load(here("data", "correct_cls_apsr.rda")) 
#load(here("data", "exp_cls_ajps.rda"))
#load(here("data", "exp_cls_apsr.rda")) 
load(here("data", "expcor_cls_ajps.rda"))
load(here("data", "expcor_cls_apsr.rda"))

result_clsAJPS <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
result_pureAJPS <- readRDS(here("output", "estimates_clsPureAJPS.RDS"))
result_expAJPS <- readRDS(here("output", "estimates_clsExpAJPS.RDS"))

result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
result_pureAPSR <- readRDS(here("output", "estimates_clsPureAPSR.RDS"))
result_expAPSR <- readRDS(here("output", "estimates_clsExpAPSR.RDS"))

#mocresult_pureAJPS <- readRDS(here("output", "estimates_moc_pureAJPS.RDS"))
mocresult_correctAJPS <- readRDS(here("output", "estimates_moc_correctAJPS.RDS")) 
#mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expAJPS.RDS"))
mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expcorAJPS.RDS"))
#mocresult_pureAPSR <- readRDS(here("output", "estimates_moc_pureAPSR.RDS"))
mocresult_correctAPSR <- readRDS(here("output", "estimates_moc_correctAPSR.RDS"))
#mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expAPSR.RDS"))
mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expcorAPSR.RDS"))

@@

In addition to incorporating uncertainty, we also assembled as much available data on democratic support as possible. 
We employed `r dcpo_input_ncyi` national opinions on democracy from `r dcpo_input_surv` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncy` opinions and `r supdem_surv` national surveys used in Claassen [-@Claassen2020a; -@Claassen2020b].^[These figures represent the survey data actually used in estimating public support for democracy; as in Claassen [-@Claassen2020a; -@Claassen2020b], countries for which two separate years of survey data were not available were excluded.]

@@

```{r result-pureAJPS}
result_pureAJPS <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
  result <- map(pure_cls_ajps, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

```{r result-expAJPS}
result_expAJPS <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
  result <- map(exp_cls_ajps, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

```{r result-pureAPSR}
result_pureAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
  result <- map(pure_cls_apsr, function(aData){ # applying to the 900 datasets
    eval(parse(text = aMod))
  })

@@

```{r result-expAPSR}
result_expAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
  result <- map(exp_cls_apsr, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

```{r num-labelAJPS, eval=TRUE}
names_coef <- c(
  "(Intercept)" = "(Intercept)",
  "plm::lag(Libdem_VD, 1:2)1" = "Democracy[t-1]",
  "plm::lag(Libdem_VD, 1:2)2"  = "Democracy[t-2]",
  "plm::lag(SupDem_trim, 1)" = "Support[t-1]",
  "plm::lag(SupDem_Democ, 1)" = "Support in Democracy",
  "plm::lag(SupDem_Autoc, 1)" = "Support in Autocracy",
  "plm::lag(lnGDP_imp, 1)" = "Log~GDP~per~capita[t-1]",
  "plm::lag(GDP_imp_grth, 1)"  = "GDP~per~capita~growth[t-1]",
  "plm::lag(Libdem_regUN, 1)" = "Regional~democracy[t-1]",
  "plm::lag(Pr_Muslim, 1)" = "Percent~Muslim[t-1]",
  "plm::lag(Res_cp_WDI_di, 1)" = "Resource~dependence[t-1]"
)
```

@@

```{r num-labelAPSR, eval=TRUE}
names_coef <- c(
  "(Intercept)" = "(Intercept)",
  "plm::lag(SupDem_trim, 1:2)1" = "Democratic\n Mood\n (t-1)",
  "plm::lag(SupDem_trim, 1:2)2" = "Democratic\n Mood\n (t-2)",
  "diff(Libdem_z, lag = 1)" = "Liberal\n Democracy\n (Difference)",
  "Libdem_z" = "Liberal\n Democracy\n (Difference)",
  "plm::lag(Libdem_z, 1)" = "Liberal\n Democracy\n (t-1)",
  "diff(Polyarchy_z, lag = 1)" = "Electoral\n Democracy\n (Difference)",
  "Polyarchy_z" = "Electoral\n Democracy\n (Difference)",
  "plm::lag(Polyarchy_z, 1)" = "Electoral\n Democracy\n (t-1)",
  "diff(Liberal_z, lag = 1)" = "Minoritarian\n Democracy\n (Difference)",
  "Liberal_z" = "Minoritarian\n Democracy\n (Difference)",
  "plm::lag(Liberal_z, 1)" = "Minoritarian\n Democracy\n (t-1)",
  "diff(lnGDP_imp, lag = 1)" = "Log GDP\n per capita\n (Difference)",
  "lnGDP_imp" = "Log GDP\n per capita\n (Difference)",
  "plm::lag(lnGDP_imp, 1)" = "Log GDP\n (t-1)",
  "diff(Corrup_TI_z, lag = 1)" = "Corruption\n (Difference)",
  "Corrup_TI_z" = "Corruption\n (Difference)",
  "plm::lag(Corrup_TI_z, 1)" = "Corruption\n (t-1)"
)
```

@@

#df_pure_clsAjps <- purrr::map(1:900, function(anEntry) {
#  pure_cls_ajps[[anEntry]] %>% 
#    plm::pdata.frame(index = c("country", "year"))
#})

@@

plot_AJPS1 <- dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms))) +
  scale_color_grey(start = 0.4, end = 0.8) +
  labs(
    title = "DV: V-Dem Liberal Democracy Index",
    subtitle = "Regime Compacted"
  ) +
  facet_wrap(~type, scales = "free_x") + 
  theme(legend.position = "none")

@@

result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
        "Support\n demo only\n (t-1)",
        "Support\n auto only\n (t-1)",
        "Log GDP\n per capita\n (t-1)",
        "GDP per\n capita growth\n (t-1)",
        "Regional\n democracy\n (t-1)",
        "Percent\n Muslim\n (t-1)",
        "Resource\n dependence\n (t-1)"),
      time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Original","Corrected", "Uncertainty+Expanded Data")))
terms2 <- factor(rev(c("Democracy[t-1]",
                       "Democracy[t-2]",
                       "Support[t-1] (democracies~only)",
                       "Support[t-1] (autocracies~only)",
                       "Log~GDP~per~capita[t-1]",
                       "GDP~per~capita~growth[t-1]",
                       "Regional~democracy[t-1]",
                       "Percent~Muslim[t-1]",
                       "Resource~dependence[t-1]")), levels =
                   rev(c("Democracy[t-1]",
                         "Democracy[t-2]",
                         "Support[t-1] (democracies~only)",
                         "Support[t-1] (autocracies~only)",
                         "Log~GDP~per~capita[t-1]",
                         "GDP~per~capita~growth[t-1]",
                         "Regional~democracy[t-1]",
                         "Percent~Muslim[t-1]",
                         "Resource~dependence[t-1]")))
plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms2))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  labs(
    title = "",
    subtitle = "Regime Specific"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "bottom", 
        legend.title = element_blank())
legend <- get_legend(plot_AJPS2)
plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
```

@@

#df_pure_clsAPSR <- purrr::map(1:900, function(anEntry) {
#  pure_cls_apsr[[anEntry]] %>% 
#    plm::pdata.frame(index = c("country", "year"))
#}
#)

@@

```{r plot-mocAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", eval = TRUE, fig.width=7, fig.height=10, eval=TRUE}

@@

terms1 <- factor(rev(c("Support[t-1]",
                       "Support[t-2]",
                       "Delta~Liberal~democracy",
                       "Liberal~democracy[t-1]",
                       "Delta~Log~GDP~per~capita",
                       "Log~GDP[t-1]")),
                 levels = rev(c("Support[t-1]",
                                "Support[t-2]",
                                "Delta~Liberal~democracy",
                                "Liberal~democracy[t-1]",
                                "Delta~Log~GDP~per~capita",
                                "Log~GDP[t-1]")))
plot_APSR1 <- dwplot(result_APSR1, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms1))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "DV: The Change of Public Support for Democracy",
    subtitle = "Regime Compacted"
  ) +
  facet_wrap(~type, drop=T,scales = "free_x") +
  theme(legend.position = "none")

@@

result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Electoral Democracy\n (Difference)",
        "Electoral Democracy\n (t-1)",
        "Minoritarian Democracy\n (Difference)",
        "Minoritarian Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)"),
      time = 3),
      rep(
        c("Electoral Democracy\n (Difference)", 
          "Minoritarian Democracy\n (Difference)",
          "Log GDP\n per capita\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Corrected", "Uncertainty+Expanded Data"))
  )
terms3 <- factor(rev(c("Support[t-1]",
                       "Support[t-2]",
                       "Delta~Electoral~democracy",
                       "Electoral~democracy[t-1]",
                       "Delta~Minoritarian~democracy",
                       "Minoritarian~democracy[t-1]",
                       "Delta~Log~GDP~per~capita",
                       "Log~GDP[t-1]")),
                 levels = rev(c("Support[t-1]",
                                "Support[t-2]",
                                "Delta~Electoral~democracy",
                                "Electoral~democracy[t-1]",
                                "Delta~Minoritarian~democracy",
                                "Minoritarian~democracy[t-1]",
                                "Delta~Log~GDP~per~capita",
                                "Log~GDP[t-1]")))
plot_RegAPSR1 <- dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms3))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "",
    subtitle = "Regime Specified"
  ) +
  facet_wrap(~type, scales = "free_x") + 
  theme(legend.position = "none")

@@

result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Liberal Democracy\n (Difference)",
        "Liberal Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)",
        "Corruption\n (Difference)",
        "Corruption\n (t-1)"
      ),
      time = 3),
      rep(
        c("Liberal Democracy\n (Difference)", 
          "Log GDP\n per capita\n (Difference)",
          "Corruption\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Corrected", "Uncertainty+Expanded Data"))
  )
terms2 <- factor(rev(c("Support[t-1]",
                       "Support[t-2]",
                       "Delta~Liberal~democracy",
                       "Liberal~democracy[t-1]",
                       "Delta~Log~GDP~per~capita",
                       "Log~GDP[t-1]",
                       "Delta~Corruption",
                       "Corruption[t-1]")),
                 levels = rev(c("Support[t-1]",
                                "Support[t-2]",
                                "Delta~Liberal~democracy",
                                "Liberal~democracy[t-1]",
                                "Delta~Log~GDP~per~capita",
                                "Log~GDP[t-1]",
                                "Delta~Corruption",
                                "Corruption[t-1]")))
plot_APSR2 <- dwplot(result_APSR2, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms2))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "",
    subtitle = "W. Corruption"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "none")

@@

result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Electoral Democracy\n (Difference)",
        "Electoral Democracy\n (t-1)",
        "Minoritarian Democracy\n (Difference)",
        "Minoritarian Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)",
        "Corruption\n (Difference)",
        "Corruption\n (t-1)"
      ),
      time = 3),
      rep(
        c("Electoral Democracy\n (Difference)", 
          "Minoritarian Democracy\n (Difference)",
          "Log GDP\n per capita\n (Difference)",
          "Corruption\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Corrected", "Uncertainty+Expanded Data"))
  )
terms4 <- factor(rev(c("Support[t-1]",
                       "Support[t-2]",
                       "Delta~Electoral~democracy",
                       "Electoral~democracy[t-1]",
                       "Delta~Minoritarian~democracy",
                       "Minoritarian~democracy[t-1]",
                       "Delta~Log~GDP",
                       "Log~GDP[t-1]",
                       "Delta~Corruption",
                       "Corruption[t-1]")),
                 levels = rev(c("Support[t-1]",
                                "Support[t-2]",
                                "Delta~Electoral~democracy",
                                "Electoral~democracy[t-1]",
                                "Delta~Minoritarian~democracy",
                                "Minoritarian~democracy[t-1]",
                                "Delta~Log~GDP",
                                "Log~GDP[t-1]",
                                "Delta~Corruption",
                                "Corruption[t-1]")))
plot_RegAPSR2 <- dwplot(result_RegAPSR2, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms4))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  labs(
    title = "",
    subtitle = "Regime Specified w. Corruption"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "bottom", 
        legend.title = element_blank())

>>>>

load(here("data", "correct_cls_ajps.rda"))
load(here("data", "correct_cls_apsr.rda")) 
load(here("data", "expcor_cls_ajps.rda"))
load(here("data", "expcor_cls_apsr.rda"))

result_clsAJPS <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
result_pureAJPS <- readRDS(here("output", "estimates_clsPureAJPS.RDS"))
result_expAJPS <- readRDS(here("output", "estimates_clsExpAJPS.RDS"))
result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
result_pureAPSR <- readRDS(here("output", "estimates_clsPureAPSR.RDS"))
result_expAPSR <- readRDS(here("output", "estimates_clsExpAPSR.RDS"))

mocresult_correctAJPS <- readRDS(here("output", "estimates_moc_correctAJPS.RDS")) 
mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expcorAJPS.RDS"))
mocresult_correctAPSR <- readRDS(here("output", "estimates_moc_correctAPSR.RDS"))
mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expcorAPSR.RDS"))

@@

[XXXX This paragraph should be revised]
In addition to incorporating uncertainty, we also assembled as much available data on democratic support as possible. 
We employed `r dcpo_input_ncyi` national opinions on democracy from `r dcpo_input_surv` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncy` opinions and `r supdem_surv` national surveys used in Claassen [-@Claassen2020a; -@Claassen2020b].^[These figures represent the survey data actually used in estimating public support for democracy; as in Claassen [-@Claassen2020a; -@Claassen2020b], countries for which two separate years of survey data were not available were excluded.]

@@

```{r result-pureAJPS}
result_pureAJPS <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
  result <- map(correct_cls_ajps, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

```{r result-expAJPS}
result_expAJPS <- map(ls_mod_ajpsCLS, function(aMod){ # reading a model
  result <- map(expcor_cls_ajps, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

```{r result-pureAPSR}
result_pureAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
  result <- map(correct_cls_apsr, function(aData){ # applying to the 900 datasets
    eval(parse(text = aMod))
  })

@@

```{r result-expAPSR}
result_expAPSR <- map(ls_mod_apsrCLS, function(aMod){ # reading a model
  result <- map(expcor_cls_apsr, function(aData){ # applying to the 1000 datasets
    eval(parse(text = aMod))
  })

@@

```{r num-labelAJPS, eval=TRUE}
names_coef <- c(
  "(Intercept)" = "(Intercept)",
  "plm::lag(Libdem_VD, 1:2)1" = "Democracy[t-1]",
  "plm::lag(Libdem_VD, 1:2)2"  = "Democracy[t-2]",
  "plm::lag(SupDem_trim, 1)" = "Support[t-1]",
  "plm::lag(SupDem_Democ, 1)" = "Support in Democracy",
  "plm::lag(SupDem_Autoc, 1)" = "Support in Autocracy",
  "plm::lag(lnGDP_imp, 1)" = "Log GDP Per Capita[t-1]",
  "plm::lag(GDP_imp_grth, 1)"  = "GDP Per Capita~growth[t-1]",
  "plm::lag(Libdem_regUN, 1)" = "Regional Democracy[t-1]",
  "plm::lag(Pr_Muslim, 1)" = "Percent Muslim[t-1]",
  "plm::lag(Res_cp_WDI_di, 1)" = "Resource Dependence[t-1]"
)
```

@@

```{r num-labelAPSR, eval=TRUE}
names_coef <- c(
  "(Intercept)" = "(Intercept)",
  "plm::lag(SupDem_trim, 1:2)1" = "Democratic Mood (t-1)",
  "plm::lag(SupDem_trim, 1:2)2" = "Democratic Mood (t-2)",
  "diff(Libdem_z, lag = 1)" = "Liberal Democracy (Difference)",
  "Libdem_z" = "Liberal Democracy (Difference)",
  "plm::lag(Libdem_z, 1)" = "Liberal Democracy (t-1)",
  "diff(Polyarchy_z, lag = 1)" = "Electoral Democracy (Difference)",
  "Polyarchy_z" = "Electoral Democracy (Difference)",
  "plm::lag(Polyarchy_z, 1)" = "Electoral Democracy (t-1)",
  "diff(Liberal_z, lag = 1)" = "Minoritarian Democracy (Difference)",
  "Liberal_z" = "Minoritarian Democracy (Difference)",
  "plm::lag(Liberal_z, 1)" = "Minoritarian Democracy (t-1)",
  "diff(lnGDP_imp, lag = 1)" = "Log GDP per capita (Difference)",
  "lnGDP_imp" = "Log GDP per capita (Difference)",
  "plm::lag(lnGDP_imp, 1)" = "Log GDP (t-1)",
  "diff(Corrup_TI_z, lag = 1)" = "Corruption (Difference)",
  "Corrup_TI_z" = "Corruption (Difference)",
  "plm::lag(Corrup_TI_z, 1)" = "Corruption (t-1)"
)
```

@@

#df_pure_clsAjps <- purrr::map(1:900, function(anEntry) {
#  correct_cls_ajps[[anEntry]] %>% 
#    plm::pdata.frame(index = c("country", "year"))
#})

@@

plot_AJPS1 <- dwplot(result_pooledAJPS, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms))) +
  labs(
    title = "DV: V-Dem Liberal Democracy Index",
    subtitle = "Regime Compacted"
  ) +
  facet_wrap(~type, scales = "free_x") + 
  theme(legend.position = "none")

@@

result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
        "Support\n demo only\n (t-1)",
        "Support\n auto only\n (t-1)",
        "Log GDP\n per capita\n (t-1)",
        "GDP per\n capita growth\n (t-1)",
        "Regional\n democracy\n (t-1)",
        "Percent\n Muslim\n (t-1)",
        "Resource\n dependence\n (t-1)"),
      time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Original","Corrected", "Uncertainty+Expanded Data")))
terms2 <- factor(rev(c("Democracy[t-1]",
                       "Democracy[t-2]",
                       "Support[t-1] (democracies~only)",
                       "Support[t-1] (autocracies~only)",
                       "Log~GDP~per~capita[t-1]",
                       "GDP~per~capita~growth[t-1]",
                       "Regional~democracy[t-1]",
                       "Percent~Muslim[t-1]",
                       "Resource~dependence[t-1]")), levels =
                   rev(c("Democracy[t-1]",
                         "Democracy[t-2]",
                         "Support[t-1] (democracies~only)",
                         "Support[t-1] (autocracies~only)",
                         "Log~GDP~per~capita[t-1]",
                         "GDP~per~capita~growth[t-1]",
                         "Regional~democracy[t-1]",
                         "Percent~Muslim[t-1]",
                         "Resource~dependence[t-1]")))
plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms2))) +
  labs(
    title = "",
    subtitle = "Regime Specific"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "bottom", 
        legend.title = element_blank())
legend <- get_legend(plot_AJPS2)
plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)
```

@@

#df_pure_clsAPSR <- purrr::map(1:900, function(anEntry) {
#  correct_cls_apsr[[anEntry]] %>% 
#    plm::pdata.frame(index = c("country", "year"))
#}
#)

@@

```{r plot-mocAPSR, fig.cap= "The Effect of Democracy on the Change of Public Support", eval = TRUE, fig.width=7, fig.height=12, eval=TRUE}

@@

terms1 <- factor(rev(c("Support[t-1]",
                       "Support[t-2]",
                       "Delta~Liberal~democracy",
                       "Liberal~democracy[t-1]",
                       "Delta~Log~GDP~per~capita",
                       "Log~GDP[t-1]")),
                 levels = rev(c("Support[t-1]",
                                "Support[t-2]",
                                "Delta~Liberal~democracy",
                                "Liberal~democracy[t-1]",
                                "Delta~Log~GDP~per~capita",
                                "Log~GDP[t-1]")))
plot_APSR1 <- dwplot(result_APSR1, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms1))) +
  labs(
    title = "DV: The Change of Public Support for Democracy",
    subtitle = "Regime Compacted"
  ) +
  facet_wrap(~type, drop=T,scales = "free_x") +
  theme(legend.position = "none")

@@

result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Electoral Democracy\n (Difference)",
        "Electoral Democracy\n (t-1)",
        "Minoritarian Democracy\n (Difference)",
        "Minoritarian Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)"),
      time = 3),
      rep(
        c("Electoral Democracy\n (Difference)", 
          "Minoritarian Democracy\n (Difference)",
          "Log GDP\n per capita\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Corrected", "Uncertainty+Expanded Data"))
  )
terms3 <- factor(rev(c("Support[t-1]",
                       "Support[t-2]",
                       "Delta~Electoral~democracy",
                       "Electoral~democracy[t-1]",
                       "Delta~Minoritarian~democracy",
                       "Minoritarian~democracy[t-1]",
                       "Delta~Log~GDP~per~capita",
                       "Log~GDP[t-1]")),
                 levels = rev(c("Support[t-1]",
                                "Support[t-2]",
                                "Delta~Electoral~democracy",
                                "Electoral~democracy[t-1]",
                                "Delta~Minoritarian~democracy",
                                "Minoritarian~democracy[t-1]",
                                "Delta~Log~GDP~per~capita",
                                "Log~GDP[t-1]")))
plot_RegAPSR1 <- dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms3))) +
  labs(
    title = "",
    subtitle = "Regime Specified"
  ) +
  facet_wrap(~type, scales = "free_x") + 
  theme(legend.position = "none")

@@

result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Liberal Democracy\n (Difference)",
        "Liberal Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)",
        "Corruption\n (Difference)",
        "Corruption\n (t-1)"
      ),
      time = 3),
      rep(
        c("Liberal Democracy\n (Difference)", 
          "Log GDP\n per capita\n (Difference)",
          "Corruption\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Corrected", "Uncertainty+Expanded Data"))
  )
terms2 <- factor(rev(c("Support[t-1]",
                       "Support[t-2]",
                       "Delta~Liberal~democracy",
                       "Liberal~democracy[t-1]",
                       "Delta~Log~GDP~per~capita",
                       "Log~GDP[t-1]",
                       "Delta~Corruption",
                       "Corruption[t-1]")),
                 levels = rev(c("Support[t-1]",
                                "Support[t-2]",
                                "Delta~Liberal~democracy",
                                "Liberal~democracy[t-1]",
                                "Delta~Log~GDP~per~capita",
                                "Log~GDP[t-1]",
                                "Delta~Corruption",
                                "Corruption[t-1]")))
plot_APSR2 <- dwplot(result_APSR2, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms2))) +
  labs(
    title = "",
    subtitle = "W. Corruption"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "none")

@@

result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Electoral Democracy\n (Difference)",
        "Electoral Democracy\n (t-1)",
        "Minoritarian Democracy\n (Difference)",
        "Minoritarian Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)",
        "Corruption\n (Difference)",
        "Corruption\n (t-1)"
      ),
      time = 3),
      rep(
        c("Electoral Democracy\n (Difference)", 
          "Minoritarian Democracy\n (Difference)",
          "Log GDP\n per capita\n (Difference)",
          "Corruption\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Corrected", "Uncertainty+Expanded Data"))
  )
terms4 <- factor(rev(c("Support[t-1]",
                       "Support[t-2]",
                       "Delta~Electoral~democracy",
                       "Electoral~democracy[t-1]",
                       "Delta~Minoritarian~democracy",
                       "Minoritarian~democracy[t-1]",
                       "Delta~Log~GDP",
                       "Log~GDP[t-1]",
                       "Delta~Corruption",
                       "Corruption[t-1]")),
                 levels = rev(c("Support[t-1]",
                                "Support[t-2]",
                                "Delta~Electoral~democracy",
                                "Electoral~democracy[t-1]",
                                "Delta~Minoritarian~democracy",
                                "Minoritarian~democracy[t-1]",
                                "Delta~Log~GDP",
                                "Log~GDP[t-1]",
                                "Delta~Corruption",
                                "Corruption[t-1]")))
plot_RegAPSR2 <- dwplot(result_RegAPSR2, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms4))) +
  labs(
    title = "",
    subtitle = "Regime Specified w. Corruption"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "bottom", 
        legend.title = element_blank())
